Response to the defense feedback

### 2021-06-15 Chapter-5/Chapter-5.tex
Updates from Overleaf

\begin{figure}[h]
  \begin{minipage}{0.45\linewidth}
    \begin{lstlisting}[numbers=none,xleftmargin=.1\textwidth,xrightmargin=.15\textwidth]
uint8_t *T = malloc(4);
if (T==NULL) exit(1);
...
t = T[i];    
\end{lstlisting}
  \end{minipage}
  \hfill
  \begin{minipage}{0.5\linewidth}
    \resizebox{\textwidth}{!}{

@@

\section{Multiple Leakages Sites}
Real-world software can have many side-channel vulnerabilities. These vulnerabilities may spread throughout the whole program. An adversary may exploit more than one side-channel vulnerabilities to gain more information~\cite{7163052, 191010}. In order to quantify the
total information leakage precisely, we need to know the relation of these leakage sites.

@@

Considering the examples in Figure~\ref{chapter5:fig:multiple}, Figure~\ref{chapter5:fig:multiple}(a) show a code snippet with two leakage sites at line 6 and line 8 respectively. For example, if an adversary observes that function \textsf{a} executes, then the attacker can infer the first byte in buffer \textsf{secret} is larger than the second byte.  Similarly, if an adversary observes that function \textsf{b} executes, then the attacker can infer that the sum of the first two bytes in buffer \textsf{secret} is smaller than $256$. The interesting part here is that if the attacker observes that function \textsf{a} executes, then he still has zero knowledge about the function \textsf{b}. The two leakage sites in Figure~\ref{chapter5:fig:multiple}(b) are different. If an attacker observes function \textsf{c} executes, then it is likely the attacker can observe that function \textsf{d} also executes.

Suppose one program has two side-channel vulnerabilities $A$ and $B$, which can leak $L_A$ and $L_B$ bits, respectively, according to Definition~\ref{chapter5:def}. 
For the example in Figure~\ref{chapter5:fig:multiple}, we use $a$ to denote that the function \textsf{a} executes, and $\lnot a$ to denote that the function \textsf{a} does not execute during the execution.
Depending on the relation between $A$ and $B$, the total leaked information $L_{\mathit{AB}}$ will be:

\subsection{Independent Leakages}
Given a leakage site $A$, the site has different memory access patterns under different secrets. We call each memory access pattern as an observation. If any observation of $A$ does not affect the probability of occurrence of any observation of $B$, we call the two leakage sites $A$ and $B$ are independent. $p_{ab} = p_ap_b$.
If $A$ and $B$ are two independent leakages, the total amount of leaked information is:
\begin{align*} 
L_{\mathit{AB}} &= - \sum_{}p_{ab}\log_2p_{ab} = - \sum_{}p_ap_b\log_2p_ap_b \\
                &= - \sum_{}p_{a}\log_2p_{a} - \sum_{}p_{b}\log_2p_{b} \\
                &= L_A + L_B
\end{align*}

\subsection{Dependent Leakages}
If A and B are dependent leakages, the total information leakage will be:
\[\max{\{L_A, L_B\}}  \leq L_{\mathit{AB}} < L_A + L_B\]

We use the chi-squared test to check if two leakage sites are independent. A chi-squared test can determine if there is a relationship between two categorical variables. Suppose we can summarize the data in a $r*c$ two-way contingency table. The chi-squared test statistic and the degrees of freedom $v$ are calculated with the below formula:
\[\tilde{\chi}^2=\sum_{k=1}^{rc} \frac{(O_k - E_k)^2}{E_k} \qquad	 v = (r - 1)(c - 1)\]
Here $O$ is the observed value, and $E$ is the expected value. A low value means that there is a high correlation between the two variables.

The null hypothesis is that the two leakages are independent.
We generate random inputs as the secret input and record the memory access for each execution. Each time, the execution is independent of the previous execution, and the target program is the same as the program executed in the previous experiment. For one type of event(e.g., function $a$ executes), we use $p$ to denote the probability of the event. Suppose the target program is executed $n$ times, the probability that we observe the event happens $k \,(k < n)$ times is $P = \binom{k}{n}p^n(1-p)^{n-k}$. Therefore, the times of the same observation for each event should satisfy the binomial distribution. After that, we can use the chi-squared test to test whether the two leakage sites are independent.

\begin{figure}[h]
  \begin{minipage}{0.45\linewidth}
      \begin{tabular}{rrrr}
        \toprule
        & $a$ & $\lnot a$  & total\\
        \midrule
        $b$   & 255 (255.5) & 253 (252.5) &   508  \\
        $\lnot b$   & 260 (259.5)  & 256 (256.5) &    516   \\
        total &   515 &  509   & 1,024   \\
        \bottomrule
      \end{tabular}\caption*{(a)}
  \end{minipage}
%\hspace{-15pt}
\hfill
%\hspace{-15pt}
  \begin{minipage}{0.45\linewidth}
      \begin{tabular}{rrrr}
        \toprule
        & $c$ & $\lnot c$  & total\\
        \midrule
        $d$   & 809 (764.8) & 82 (126.2) & 891    \\
        $\lnot d$   & 70 (114.2)  & 63 (18.8)&  133     \\
        total &  879 &  145  & 1,024    \\
        \bottomrule
      \end{tabular}\caption*{(b)}
  \end{minipage}
  \caption{The contingency table for the experiments. The numbers in the bracket are expected values. }\label{chapter5:fig:con_table}
\end{figure}

Assume we generate $1024$ random inputs and record the memory access each time.  After calculating the number of the same observation, we get the contingency table shown in Figure~\ref{chapter5:fig:con_table}. Suppose the observations of the execution of function \textsf{a} and the execution of function \textsf{b} are independent ($p_{ab} = p_a*p_b$),  we calculate the expected value for the observation $ab$ based on the frequency.
\[ E_{ab} = 1024*p_{ab} = 1024*p_a*p_b = 1024*\frac{515}{1024}*\frac{508}{1024} = 255.5\]
Similarly, we calculate the rest expected values with the hypothesis that the leakages are independent and fill in them in Figure~\ref{chapter5:fig:con_table}. The degree of freedom $v$ is $(2-1)*(2-1) = 1$.

@@

\subsubsection{Estimate The Leaked Information}
According to Definition~\ref{chapter5:def}, we quantify the information leakage based on the distribution of the observation. If we calculate the information leakage from a $4MB$ memory area, then the length of the byte-level bitmap is $4*1024*1024 = 4194304$. While it is possible to compute the distribution of the bitmap theoretically, it is hard to compare the bitmap of such length in practice.

@@

\begin{displaymath}
  H(O') = - \frac{3}{8}*\log_2{\frac{3}{8}}- \frac{1}{2}*\log_2{\frac{1}{2}}
  - \frac{1}{8}*\log_2{\frac{1}{8}} = 1.4 \,\mathrm{bits}
\end{displaymath}

>>>>

\begin{figure}[h]
  \begin{minipage}{0.45\linewidth}
    \begin{lstlisting}[numbers=none,xleftmargin=.1\textwidth,xrightmargin=.15\textwidth]
uint8_t* T = malloc(4);
if (T==NULL) exit(1);
...
t = T[i];    
\end{lstlisting}
  \end{minipage}
  \hfill
  \begin{minipage}{0.5\linewidth}
    \resizebox{\textwidth}{!}{

@@

\section{Multiple Leakages Sites}
Real-world software can have many side-channel vulnerabilities. These vulnerabilities may spread throughout the whole program. An adversary may exploit more than one side-channel vulnerability to gain more information~\cite{7163052, 191010}. In order to quantify the
total information leakage precisely, we need to know the relation of these leakage sites.

@@

Considering the examples in Figure~\ref{chapter5:fig:multiple}, Figure~\ref{chapter5:fig:multiple}(a) show a code snippet with two leakage sites at line 6 and line 8, respectively. For example, if an adversary observes that function \textsf{a} executes, then the attacker can infer that the first byte in buffer \textsf{secret} is larger than the second byte.  Similarly, if an adversary observes that function \textsf{b} executes, then the attacker can infer that the sum of the first two bytes in buffer \textsf{secret} is smaller than $256$. The interesting part here is that if the attacker observes that function \textsf{a} executes, then he still has zero knowledge about the function \textsf{b}. The two leakage sites in Figure~\ref{chapter5:fig:multiple}(b) are different. If an attacker observes function \textsf{c} executes, then it is likely the attacker can observe that function \textsf{d} also executes.

Suppose a program has two side-channel vulnerabilities $A$ and $B$, which can leak $L_A$ and $L_B$ bits, respectively, according to Definition~\ref{chapter5:def}. 
For the example in Figure~\ref{chapter5:fig:multiple}, we use $a$ to denote that the function \textsf{a} executes, and $\lnot a$ to denote that the function \textsf{a} does not execute during the execution.
Depending on the relation between $A$ and $B$, the total leaked information $L_{\mathit{AB}}$ can be calculated as follows.

\subsection{Independent Leakages}
Given a leakage site $A$, the site has different memory access patterns under different secrets. We call each memory access pattern as an observation. If any observation of $A$ does not affect the probability of occurrence of any observation of $B$, we call the two leakage sites $A$ and $B$ are independent, $p_{ab} = p_ap_b$.
If $A$ and $B$ are two independent leakages, the total amount of leaked information is:
\begin{align*} 
L_{\mathit{AB}} &= - \sum_{}p_{ab}\log_2p_{ab} = - \sum_{}p_ap_b\log_2p_ap_b \\
                &= - \sum_{}p_{a}\log_2p_{a} - \sum_{}p_{b}\log_2p_{b} \\
                &= L_A + L_B
\end{align*}

\subsection{Dependent Leakages}
If $A$ and $B$ are dependent leakages, the total information leakage will be:
\[\max{\{L_A, L_B\}}  \leq L_{\mathit{AB}} < L_A + L_B\]

We use the chi-squared test to check if two leakage sites are independent. A chi-squared test can determine if there is a relationship between two categorical variables. Suppose we can summarize the data in a $r \cdot c$ two-way contingency table. The chi-squared test statistic and the degrees of freedom $v$ are calculated with the formula below.
\[\tilde{\chi}^2=\sum_{k=1}^{rc} \frac{(O_k - E_k)^2}{E_k} \qquad and	 v = (r - 1)(c - 1)\]
Here $O$ is the observed value and $E$ is the expected value. A low value means that there is a high correlation between the two variables.

The null hypothesis is that the two leakages are independent.
We generate random inputs as the secret input and record the memory access for each execution. Each time, the execution is independent of the previous execution, and the target program is the same as the program executed in the previous experiment. For one type of event (e.g., function $a$ executes), we use $p$ to denote the probability of the event. Suppose the target program is executed $n$ times, the probability that we observe the event happens $k \,(k < n)$ times is $P = \binom{k}{n}p^n(1-p)^{n-k}$. Therefore, the times of the same observation for each event should satisfy the binomial distribution. After that, we can use the chi-squared test to test whether the two leakage sites are independent.

\begin{figure}[h]
  \begin{minipage}{0.46\linewidth}
      \begin{tabular}{rrrr}
        \toprule
        & $a$ & $\lnot a$  & total\\
        \midrule
        $b$   & 255 (255.5) & 253 (252.5) &   508  \\
        $\lnot b$   & 260 (259.5)  & 256 (256.5) &    516   \\
        total &   515 &  509   & 1,024   \\
        \bottomrule
      \end{tabular}\caption*{(a)}
  \end{minipage}
\hfill
  \begin{minipage}{0.46\linewidth}
      \begin{tabular}{rrrr}
        \toprule
        & $c$ & $\lnot c$  & total\\
        \midrule
        $d$   & 809 (764.8) & 82 (126.2) & 891    \\
        $\lnot d$   & 70 (114.2)  & 63 (18.8)&  133     \\
        total &  879 &  145  & 1,024    \\
        \bottomrule
      \end{tabular}\caption*{(b)}
  \end{minipage}
  \caption{The contingency table for the experiments. The numbers in the parenthesis are expected values. }\label{chapter5:fig:con_table}
\end{figure}

Assume we generate $1024$ random inputs and record the memory access each time.  After calculating the number of the same observation, we get the contingency table shown in Figure~\ref{chapter5:fig:con_table}. Suppose the observations of the execution of function \textsf{a} and the execution of function \textsf{b} are independent ($p_{ab} = p_a \cdot p_b$),  we calculate the expected value for the observation $ab$ based on the frequency.
\[ E_{ab} = 1024 \cdot p_{ab} = 1024\cdot p_a \cdot p_b = 1024  \cdot \frac{515}{1024} \cdot \frac{508}{1024} = 255.5\]
Similarly, we calculate the rest expected values with the hypothesis that the leakages are independent and fill in them in Figure~\ref{chapter5:fig:con_table}. The degree of freedom $v$ is $(2-1)\cdot(2-1) = 1$.

@@

\subsubsection{Estimate The Leaked Information}
According to Definition~\ref{chapter5:def}, we quantify the information leakage based on the distribution of the observation. If we calculate the information leakage from a $4MB$ memory area, then the length of the byte-level bitmap is $4 \cdot 1024 \cdot 1024 = 4194304$. While it is possible to compute the distribution of the bitmap theoretically, it is hard to compare the bitmap of such length in practice.

@@

\begin{displaymath}
  H(O') = - \frac{3}{8} \cdot \log_2{\frac{3}{8}}- \frac{1}{2} \cdot \log_2{\frac{1}{2}}
  - \frac{1}{8} \cdot \log_2{\frac{1}{8}} = 1.4 \,\mathrm{bits}
\end{displaymath}
